MSstatsPTM statistical relative quantification of post-translational modifications in bottom-up proteomic experiments

### 2022-03-21 main/MSstatsPTM_Main.tex
Small

\todo{in Figure 2 b, there are two quantities of interest, stated at the population level. Describe the quantities, what is of interest, why relevant}

@@

\medskip \noindent {\bf Limma} \todo{Could you fine-tune, using the same order as above for Limma? I.e., null hypothesis, the data, the model, the inference} Modifications of the $t$-test such as moderated $t$-test with Limma were also proposed~\cite{Ritchie_15a}\cite{Zhu}. While simple, these approaches do not fully account for the sources of variations, and are not directly applicable to experiments with complex designs, e.g., comparisons of multiple conditions, acquisition in multiple batches, etc. Additionally, while these approaches can be applied to experiments studying PTMs, there is not a self contained, straight forward implementation of the methods, making application challenging.

>>>>

\todo{in Figure 2 b, there are two quantities of interest, stated at the population level. Describe the quantities, what is of interest, why relevant. It may help to introduce multiple versions of the null hypotheses, to contrast the methods below} \todo{Also please edit the figure caption}

@@

\medskip \noindent {\bf Limma} \todo{Could you fine-tune, using the same order as above for Limma? I.e., null hypothesis, the data, the model, the inference. I think the text can be made more compact, and a bit more technical, by directly referring to either Fig 1 or the equations above} Modifications of the $t$-test such as moderated $t$-test with Limma were also proposed~\cite{Ritchie_15a}\cite{Zhu}. While simple, these approaches do not fully account for the sources of variations, and are not directly applicable to experiments with complex designs, e.g., comparisons of multiple conditions, acquisition in multiple batches, etc. Additionally, while these approaches can be applied to experiments studying PTMs, there is not a self contained, straight forward implementation of the methods, making application challenging.
